\documentclass{article}
\usepackage[utf8]{inputenc}

\title{CPSC463 Final Part 2}
\author{Tanner Hammond}
\date{December 2021}

\begin{document}

\maketitle
2. Multiple-selection statements:\\
Form and type of the expression that controls a selection. \\
How selectable segments are specified. \\
Is execution flow restricted to include just a single selectable segment. In C++ it's just a single segment.\\
How case values are specified. \\
How should unrepresented selector expression values be handled if at all. \\

3. Counter-Controlled loops:\\
Type and scope of loop variable. The scope of loop variables in C++ are limited to the loop if defined in the loop parameters. The type of counter-controlled loop variables are types like integers, doubles, and floats.\\
Legal for loop variable or parameter to be changed in the loop and does it affect loop control. In C++ the loop variable can be changed inside the loop. The parameters can't be changed in the loop. Changing the loop variable does have an effect.\\
Should loop parameters be evaluated once or once every iteration. In C++, they are evaluated once every iteration.\\
Value of loop variable after termination. In C++, if the loop variable is defined outside of the loop parameters it keeps the same value it had on loop termination. If it was defined in the loop parameters, the it has the same value but it's outside of its scope.\\

4. Pass by value: value- 2 list- \{3,1,5,7,9\} \\
Pass by reference: value- 2 list- \{3,1,5,7,9\}\\
Pass by value result: value- 2 list- \{3,1,5,7,9\}\\

5. You want them to be private so they can't be altered besides from any given functions.\\

6. Object Oriented languages:\\
Single and multiple inheritance. This is about if more than on parent is allowed or only one. In C++, only one parent is allowed.\\
Allocation and deallocation of objects. When and how the allocation and deallocation is done in the language. \\
Dynamic and static binding. Is binding done at run-time or before run-time? C++ has static binding.\\
Nested classes. Are nested classes allowed in the language? C++ doesn't allow nested classes.\\



\end{document}
